Chicago Crime Rates Prediction

### 2022-05-31 chicago_project/report_latex/article.tex
report

\subsection{Theory building}
\label{theorybuilding}
    Starting with the dataset\cite{dataset}, the research is going to begin with data exploration,
    in order to see how the data looks like. Viewing the different features the dataset has and the missing
    values, it will help to formulate a theory that will need to be proven.
    After removing or extrapolating the missing values, different parts of the data can be plotted in order
    to gain more insight into how the data is looking.
\subsection{System development}
\label{systemdevelopment}
    Next part is the System development, which involes createing new features to the dataset (feature engineering),
    converting the one type of data to another (for example date and time to UNIX timestamp).
    After that models are selected for experimantation with the newly build data.
\subsection{Observation}
\label{observation}
    The Observation happens after each model is trained. By examining the result a decision needs to be made
    to choose  which model performs the best in the given conditions with the given parameters.
\subsection{Experimentation}
\label{experimentation}
    After observation the research is continued by making small adjustments to the model parameters and the dataset
    in order to see what changes will take place and how will they influence the results.

>>>>

\subsection{Theory building}
\label{theorybuilding}
    Starting with the dataset\cite{dataset}, the research is going to begin with data exploration,
    in order to see how the data looks like. Viewing the different features the dataset has and the missing
    values, it will help to formulate a theory that will need to be proven.
    After removing or extrapolating the missing values, different parts of the data can be plotted in order
    to gain more insight into how the data is looking.
\subsection{System development}
\label{systemdevelopment}
    Next part is the System development, which involes creating new features to the dataset (feature engineering),
    converting the one type of data to another (for example date and time to UNIX timestamp).
    After that models are selected for experimantation with the newly build data.
\subsection{Observation}
\label{observation}
    The Observation happens after each model is trained. By examining the result a decision needs to be made
    to choose  which model performs the best in the given conditions with the given parameters.
\subsection{Experimentation}
\label{experimentation}
    After observation the research is continued by making small adjustments to the model parameters and the dataset
    in order to see what changes will take place and how will they influence the results.
